Regression

### 2017-11-25 paper/R/03_stm.Rmd
some cleaning

rm(list=ls())
# Functions
source("func/02-topic-modelling-functions.R")

```{r caching, echo = FALSE}
load("../output/models/STM 40 .Rda")
#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)

#btw$articleID <- rownames(btw)
```

## Explore Dataset
```{r}
library(RColorBrewer)

col <- brewer.pal(6,"Dark2")
```

```{r}
btw %>%
  group_by(date, site) %>%
  summarise(obs = n()) %>%
  ggplot(aes(date, obs, color = site)) +
  geom_line() +
  scale_color_manual(values = col) +
  theme(legend.position="none") +
  labs(x="", y="Count",color="")

#ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
#       dpi = 600)
```

```{r}
btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col, alpha= .8) +
  labs(x="", y="Count")

#ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
#       dpi = 600)
```

```{r}
btw %>%
  ggplot(aes(date, site, size=fb_shares, color = site)) +
  geom_point(show.legend = FALSE, alpha = .8) +
  scale_color_manual(values = col) +
  labs(x="", y="")

#ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
#       dpi = 600)

btw %>%
  filter(site == "bild.de") %>%
  select(title, text, fb_shares) %>%
  .[3,] %>%
  htmlTable::htmlTable()
```

```{r}
btw %>%
  ggplot(aes(site, fb_shares)) +
  stat_summary(fun.y="mean", geom="bar", fill = col, alpha = .8) +
  labs(x="", y="")

@@

```{r Tokenize}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") %>%
  # Remove short words
  filter(str_length(word) >= 3) ->
  # Assign to variable
  posts_tokenized.dt

@@

## Structural Topic Model

```{r eval=FALSE, include=FALSE}
# Build Corpus
btw$month <- month(btw$date)
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

We then train the Structural Topic Model on the full dataset, with $k = 40$.

```{r eval=FALSE, include=FALSE}
k = 40 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=k, 
           prevalence = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

#### Topic Labeling

```{r Extract wtp and dtp}

# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp

@@

```{r Compute relevance}

posts.wtp %>%
    filter(str_length(term) >= 3) %>%
  # Compute lambda and phi_kw
  mutate(lambda = 0.6, phi_kw = beta) %>% 
  # Compute and join the p_w
  left_join(
    posts_tokenized.dt %>%
      group_by(word) %>% 
      dplyr::summarise(frequency = sum(term_frequency)) %>% 
      ungroup() %>% 
      mutate(p_w = frequency/sum(frequency)) %>% 
      select(-frequency),
    by = c("term" = "word")
  ) %>%
  # Compute the relevance
  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w)) ->
  word_relevance.dt

@@

doctopics.df <- theta %>%
  transmute(articleID = rownames(.),
    topic = as.numeric(gsub("V","",topic)))

# Add Topic to origian DF
btw %>%
  inner_join(.,doctopics.df, by="articleID") %>%
  ## Combine with Topic label
  left_join(., topicLabel %>%
              select(topic_name, topic) %>%
              mutate(topic = as.numeric(topic)), by="topic") -> btw2

# subset  
topics_mapping.dt <- btw2 %>%
  group_by(topic) %>%
  slice(1) %>%
  select(topic, title.text, articleID, topic_name) 
```

## Topic Summary
```{r}
plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
         main = "Online News Topics", text.cex = 0.8)
```

@@

posts_classification.sdt <-
  posts.dtp %>% 
  group_by(articleID = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>% 
  inner_join(btw2 %>% select(title, articleID) %>%
               mutate(articleID = as.numeric(articleID)), by = "articleID") %>% 
  inner_join(topics_mapping.dt, by = "topic") %>%
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>%
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(7) %>% 
  mutate(row = row_number()) %>% 
  ungroup()

@@

ggsave(
  plot = {
    posts_classification.sdt %>% 
      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
      facet_wrap(~topic_title, ncol = 5) +
      geom_text(
        aes(label = title),
        size = 2, hjust = 0, family = "Roboto"
      ) +
      geom_point(aes(x = -0.025), size = 0.5) +
      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
      scale_color_manual(
        values = rainbow(40) %>% 
          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
      ) +
      theme(
        axis.title       = element_blank(),
        axis.text        = element_blank(),
        axis.ticks       = element_blank(),
        panel.grid       = element_blank(),
        strip.background = element_blank(),
        panel.border     = element_blank(),
        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
        plot.background  = element_rect(fill = "#FAFAFA"),
        legend.position  = "none"
      ) 
  },
  device = "png",
  filename = "../figs/topic-classification-sample.png",
  dpi = 600, height = 10, width = 16
)

@@

    ggsave(
      plot = {
        topic_labelling_top30words.dt %>% 
          ggplot(aes(x = x, y = y)) +
          geom_text_repel(
            aes(label = term, 
                color = factor(topic, levels = 1:40), 
                size = phi_kw * p_w), 
            lineheight = 0.6, 
            segment.size = NA,
            box.padding = unit(0, "lines"),
            force = 0.05,
            family = "Roboto"
          ) +
          geom_text_repel(
            data = topic_labelling_topics.dt,
            aes(label = str_wrap(topic_name, 15),
                color = factor(topic, levels = 1:40)),
            size = 2.25, lineheight = 0.7,
            segment.size = 0.5, alpha = 0.7,
            family = "Roboto", fontface = 2,
            force = 0.3
          ) +
          scale_size_continuous(range = c(1, 4)) +
          scale_color_manual(
            values = rainbow(40) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
          theme(
            axis.title = element_blank(),
            axis.text  = element_blank(),
            axis.ticks = element_blank(),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            plot.background = element_rect(fill = "#FAFAFA"),
            legend.position = "none"
          ) +
          labs(
            title    = ""
          )
      },
      filename = "../figs/news-landscape-map.png",
      device = "png",
      dpi = 600
    )

@@

@@

set.seed(7292)
posts_classification.dt %>% 
  # Add post information
  inner_join(
    btw2 %>% 
      mutate(document = as.numeric(articleID)) %>%
      select(document, date, 
             title) %>% 
      mutate(post_period = 
               date %>% 
               with_tz("Europe/Paris") %>% 
               floor_date("week")),
    by = "document"
  ) %>% 
  # Add topic information
  left_join(topics_mapping.dt, by = "topic") %>%
  # Summarise into tidy dataframe
  group_by(post_period, topic_name) %>% 
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0("<li>", sample(title, 4, replace = TRUE ), "</li>", collapse = "<br>")
  ) %>% 
  ungroup() %>% 
  mutate(
    tooltip_text = 
      paste0(
        "<b>", topic_name, "</b> in period of <b>", post_period, "</b><br>",
        "<b>Number of Articles:</b> ", comma(round(articles, 0)), "<br>",
        "<b>Sample Articles:</b><br><ul>", sample_articles, "</ul>"
      )
  ) %>% 
  # Mark peaks 
  group_by(topic_name) %>% 
  mutate_at(
    vars(articles), 
    funs(mean = mean(.), sd = sd(.), zscore = (. - mean(.))/sd(.))
  ) %>% 
  ungroup() %>% 
  mutate_at(
    vars(ends_with("zscore")),
    funs(peak = . >	1.96)
  ) %>% 
  mutate(tooltip_text = str_replace_all(tooltip_text, "'", "")) ->
  chart_topic_trends.dt
```

```{r}
chart_topic_trends.dt %>% 
    ggplot(
      aes(
        x = post_period, 
        y = factor(
          topic_name, 
          chart_topic_trends.dt %>% 
            group_by(topic_name) %>% 
            summarise(post_period = mean(post_period[peak], na.rm = TRUE)) %>% 
            ungroup() %>% 
            arrange(desc(post_period)) %$%
            unique(topic_name)
        )
      )
    ) +
    geom_tile_interactive(aes(tooltip = tooltip_text, fill = log(articles))) +
    geom_point_interactive(
      mapping = aes(tooltip = tooltip_text),
      data = chart_topic_trends.dt %>% filter(peak),
      color = "red"
    ) +
    scale_fill_viridis(
      labels = function(x) comma(round(exp(x))), 
      name = "Number of Articles",
      option = "plasma"
    ) +
    scale_x_datetime(expand = c(0, 0)) +
    labs(
      title = "", 
      caption = "
  Red dots indicate weeks where the number of articles exceeds 1.96 SD above mean for that topic
      " ) +
    theme(
      legend.position   = "bottom",
      legend.key.width  = unit(0.05, "npc"),
      legend.background = element_rect("#fafafa"),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title        = element_blank(),
      axis.ticks        = element_blank(),
      axis.text.y       = element_text(size = 8)
    )

@@

### Facebook Shares
```{r Facebook Shares}
btw %>%
  ggplot(aes(as.factor(topic), fb_shares)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha=.7) +
  labs(x="", y="Sum") +
  scale_x_discrete(breaks=c(1:40), labels = topicLabel$topic_name) +
  theme(axis.text.x = element_text(size=6, angle=90),
        axis.text.y = element_text(size=7))

>>>>

rm(list=ls())
# Functions
source("func/02-topic-modelling-functions.R")
```

```{r caching, echo=, message=FALSE, warning=FALSE}
load("../output/btw_combined.Rda")

#load("../output/models/STM 50 .Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)
```

## Explore Dataset
```{r}
library(RColorBrewer) 
col <- brewer.pal(7,"Dark2")
```

```{r message=FALSE, warning=FALSE}
btw %>%
  group_by(date, site) %>%
  summarise(obs = n()) %>%
  ggplot(aes(date, obs, color = site)) +
  geom_line() +
  scale_color_manual(values = col) +
  theme(legend.position="none") +
  labs(x="", y="Count",color="") +
  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))

# ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
#        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col, alpha= .8) +
  labs(x="", y="Count")

# ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
#        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
btw %>%
  ggplot(aes(date, site, size=text_length, color = site)) +
  geom_point(show.legend = FALSE, alpha = .8) +
  scale_color_manual(values = col) +
  labs(x="", y="")

# ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
#        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
btw %>%
  ggplot(aes(site, text_length)) +
  stat_summary(fun.y="median", geom="bar", fill = col, alpha = .8) +
  labs(x="", y="")

@@

# Structural Topic Model
## Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Select number of topics
```{r}
K<-c(30,40,50,60,80)

t1 <- Sys.time()
kresult <- searchK(out$documents, out$vocab, K, prevalence=~site + s(btw_dummy), data = out$meta, init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(btw, out, kresult, file="../output/models/kresult.Rda")
#load(file="../output/models/kresult.Rda")
```

```{r}
plot(kresult)
```

We then train the Structural Topic Model on the full dataset, with $k = 50$.

```{r}
k = 40 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents,
           vocab = out$vocab,
           K=k,
           prevalence = ~site+s(month),
           data=out$meta,
           max.em.its = 75,
           seed =8458159,
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

#load(file=paste("../output/models/STM",k,".Rda"))
```

## Explore Model Results

### Using build-in functions
#### Topic Summary
```{r}
plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
         main = "Online News Topics", text.cex = 0.8)
```

The most frequent words in the model such as for topics #3, #7, and #20
```{r}
plot(stmOut, type="labels", topics=c(37,8))
```

A comparison of two topics 
```{r}
plot(stmOut, type="perspectives", topics=c(37,8))
```

The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata). First, users must specify the variable that they wish to use for calculating an effect. If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median. These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups
```{r}
out$meta$site <- as.factor(out$meta$site)
prep <- estimateEffect(1:50 ~ site+s(month), stmOut, meta=out$meta, uncertainty = "Global")
```

To see how prevalence of topics differs across values of a continuous covariate:
```{r}
plot(prep, "month", method="continuous", topics = c(46,42),
     xlab="Month (2017)")
monthseq <- seq(from=as.Date("2017-06-01"), to=as.Date("2017-11-01"), by="month")
monthnames <- month(monthseq)
axis(1, at=as.numeric(monthseq), labels = monthnames)
```

#### Topic Labeling
```{r Tokenize}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") %>%
  # Remove short words
  filter(str_length(word) >= 3) ->
  # Assign to variable
  posts_tokenized.dt

@@

```{r Extract wtp and dtp}
# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp

@@

```{r Compute relevance}
posts.wtp %>%
    filter(str_length(term) >= 3) %>%
  # Compute lambda and phi_kw
  mutate(lambda = 0.6, phi_kw = beta) %>% 
  # Compute and join the p_w
  left_join(
    posts_tokenized.dt %>%
      group_by(word) %>% 
      dplyr::summarise(frequency = sum(term_frequency)) %>% 
      ungroup() %>% 
      mutate(p_w = frequency/sum(frequency)) %>% 
      select(-frequency),
    by = c("term" = "word")
  ) %>%
  # Compute the relevance
  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w)) ->
  word_relevance.dt

@@

doctopics.df <- theta %>%
  transmute(articleID = as.numeric(rownames(.)),
    topic = as.numeric(gsub("V","",topic)))

# Add Topic to origian DF
btw %>%
  inner_join(.,doctopics.df, by="articleID") %>%
  ## Combine with Topic label
  left_join(., topicLabel %>%
              select(topic_name, topic) %>%
              mutate(topic = as.numeric(topic)), by="topic") -> btw

# subset  
topics_mapping.dt <- btw %>%
  group_by(topic) %>%
  slice(5) %>%
  select(topic, articleID, topic_name)
```

@@

posts_classification.sdt <-
  posts.dtp %>% 
  group_by(articleID = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>%
  inner_join(btw %>% select(title, title_text, articleID, topic_name),
              by = "articleID") %>%
  #inner_join(topics_mapping.dt, by = "topic") %>%
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>%
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(7) %>% 
  mutate(row = row_number()) %>% 
  ungroup()

@@

ggsave(
  plot = {
    posts_classification.sdt %>% 
      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
      facet_wrap(~topic_title, ncol = 5) +
      geom_text(
        aes(label = title),
        size = 2, hjust = 0, family = "Roboto"
      ) +
      geom_point(aes(x = -0.025), size = 0.5) +
      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
      scale_color_manual(
        values = rainbow(50) %>% 
          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
      ) +
      theme(
        axis.title       = element_blank(),
        axis.text        = element_blank(),
        axis.ticks       = element_blank(),
        panel.grid       = element_blank(),
        strip.background = element_blank(),
        panel.border     = element_blank(),
        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
        plot.background  = element_rect(fill = "#FAFAFA"),
        legend.position  = "none"
      ) 
  },
  device = "png",
  filename = "../figs/topic-classification-sample.png",
  dpi = 600, height = 10, width = 16
)

@@

    ggsave(
      plot = {
        topic_labelling_top30words.dt %>% 
          ggplot(aes(x = x, y = y)) +
          geom_text_repel(
            aes(label = term, 
                color = factor(topic, levels = 1:40), 
                size = phi_kw * p_w), 
            lineheight = 0.6, 
            segment.size = NA,
            box.padding = unit(0, "lines"),
            force = 0.05,
            family = "Roboto"
          ) +
          geom_text_repel(
            data = topic_labelling_topics.dt,
            aes(label = str_wrap(topic_name, 15),
                color = factor(topic, levels = 1:40)),
            size = 2.25, lineheight = 0.7,
            segment.size = 0.5, alpha = 0.7,
            family = "Roboto", fontface = 2,
            force = 0.3
          ) +
          scale_size_continuous(range = c(1, 4)) +
          scale_color_manual(
            values = rainbow(39) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
          theme(
            axis.title = element_blank(),
            axis.text  = element_blank(),
            axis.ticks = element_blank(),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            plot.background = element_rect(fill = "#FAFAFA"),
            legend.position = "none"
          ) +
          labs(
            title    = ""
          )
      },
      filename = "../figs/news-landscape-map.png",
      device = "png",
      dpi = 600
    )

@@

```{r}
btw %>%
  #filter(topic==4) %>%
  filter(startsWith(title,"News")) %>%
  select(url,title, text)
```

@@

set.seed(7292)
posts_classification.dt %>% 
  # Add post information
  inner_join(
    btw %>% 
      mutate(document = as.numeric(articleID),
             date = as.POSIXct(date)) %>%
      select(document, date, 
             title) %>% 
      mutate(post_period = 
               date %>% 
               with_tz("Europe/Paris") %>% 
               floor_date("week")),
    by = "document"
  ) %>% 
  # Add topic information
  left_join(topics_mapping.dt, by = "topic") %>%
  # Summarise into tidy dataframe
  group_by(post_period, topic_name) %>% 
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0("<li>", sample(title, 4, replace = TRUE ), "</li>", collapse = "<br>")
  ) %>% 
  ungroup() %>% 
  mutate(
    tooltip_text = 
      paste0(
        "<b>", topic_name, "</b> in period of <b>", post_period, "</b><br>",
        "<b>Number of Articles:</b> ", comma(round(articles, 0)), "<br>",
        "<b>Sample Articles:</b><br><ul>", sample_articles, "</ul>"
      )
  ) %>% 
  # Mark peaks 
  group_by(topic_name) %>% 
  mutate_at(
    vars(articles), 
    funs(mean = mean(.), sd = sd(.), zscore = (. - mean(.))/sd(.))
  ) %>% 
  ungroup() %>% 
  mutate_at(
    vars(ends_with("zscore")),
    funs(peak = . >	1.96)
  ) %>% 
  mutate(tooltip_text = str_replace_all(tooltip_text, "'", "")) ->
  chart_topic_trends.dt
```

```{r message=FALSE, warning=FALSE}
chart_topic_trends.dt %>% 
    ggplot(
      aes(
        x = post_period, 
        y = factor(
          topic_name, 
          chart_topic_trends.dt %>% 
            group_by(topic_name) %>% 
            summarise(post_period = mean(post_period[peak], na.rm = TRUE)) %>% 
            ungroup() %>% 
            arrange(desc(post_period)) %$%
            unique(topic_name)
        )
      )
    ) +
    geom_tile_interactive(aes(tooltip = tooltip_text, fill = log(articles))) +
    geom_point_interactive(
      mapping = aes(tooltip = tooltip_text),
      data = chart_topic_trends.dt %>% filter(peak),
      color = "red"
    ) +
    scale_fill_viridis(
      labels = function(x) comma(round(exp(x))), 
      name = "Number of Articles",
      option = "plasma"
    ) +
    scale_x_datetime(expand = c(0, 0)) +
    labs(
      title = "", 
      caption = "
  Red dots indicate weeks where the number of articles exceeds 1.96 SD above mean for that topic
      " ) +
    theme(
      legend.position   = "bottom",
      legend.key.width  = unit(0.05, "npc"),
      legend.background = element_rect("#fafafa"),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title        = element_blank(),
      axis.ticks        = element_blank(),
      axis.text.y       = element_text(size = 8)
    )

@@

### Facebook Shares
```{r Facebook Shares}
btw2 %>%
  ggplot(aes(as.factor(topic), fb_shares)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha=.7) +
  labs(x="", y="Sum") +
  scale_x_discrete(breaks=c(1:50), labels = topicLabel$topic_name) +
  theme(axis.text.x = element_text(size=7, angle=90),
        axis.text.y = element_text(size=7))

### 2017-11-25 paper/R/04_regression.Rmd
some cleaning

## Load Data
```{r caching, echo = FALSE}
load("../output/btw_combined.Rda")
btw2 <- btw

@@

@@

```{r}
btw.reg <- 
  btw %>%
  left_join(., btw2 %>%
              select(title.text, shares, url),
            by = "title.text")
```

```{r}
# filter documents with low posterior
btw.reg <- 
  btw.reg %>%
  mutate(document = as.numeric(articleID)) %>%
  left_join(., top_topics, by="document") %>%
  filter(gamma > 0.5)

>>>>

## Load Data
```{r caching, echo = FALSE}
load("../output/btw_combined.Rda")

@@

Have a look at the assigned topics per documents
```{r}
btw$articleID <- as.numeric(rownames(btw))

# filter documents with low posterior
btw.reg <- 
  btw %>%
  mutate(document = articleID) %>%
  left_join(., top_topics, by="document")

btw.reg %>%
  filter(site=="focus.de") %>%
  group_by(topic, site) %>%
  arrange(desc(gamma)) %>%
  select(title, topic, gamma, url) %>%
  top_n(2) %>%
  htmlTable::htmlTable()
```

@@

```{r}
# filter documents with low posterior
btw.reg <- 
  btw %>%
  mutate(document = articleID) %>%
  left_join(., top_topics, by="document") 
  filter(gamma > 0.5)
